---
title: "usRbility"
# author:
#   - name: Jonathan M. Mang
#     email: jonathan.mang@uk-erlangen.de
#     institute: [er_diz, er_fak]
# institute:
#   - er_diz: Medical Center for Information and Communication Technology, Universitätsklinikum Erlangen, Erlangen, Germany.
#   - er_fak: Chair of Medical Informatics, Friedrich-Alexander-University Erlangen-Nürnberg (FAU), Erlangen, Germany.
output: 
  github_document:
    toc: true
bibliography: references.bib
link-citations: true
# csl: ios-press-books.csl
csl: ieee.csl
# styles from https://github.com/citation-style-language/styles
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

<!-- badges: start -->

[![codecov](https://codecov.io/gh/joundso/usRbility/branch/master/graph/badge.svg)](https://codecov.io/gh/joundso/usRbility)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/usRbility)](https://cran.r-project.org/package=usRbility)
[![Cran Checks](https://cranchecks.info/badges/worst/usRbility)](https://cran.r-project.org/web/checks/check_results_usRbility.html)

<!-- badges: end -->

The R package `usRbility` provides functions usefully to create questionnaires and evaluate them using common usability scales or toolings with the goal to measure a systems usability.

## Installation

<!---
You can install `usRbility` directly from CRAN:

```r
install.packages("usRbility")
```
-->

The development version can be installed using

```r
install.packages("devtools")
devtools::install_github("joundso/usRbility", ref = "master")
```

## Basic functions

### Get all currently implemented usability toolings

```{r list_toolings}
usRbility::get_all_systems()
```

## Implemented Usability Scores and Toolings

### System Usability Scale (SUS)

The System Usability Scale originally was described in 1986 and consists of `r get_sus_questions()[,.N]` questions [@brooke1996].

Its questions are:

<!-- ```{r list_sus_questions, results='asis'} -->
<!-- for (q in usRbility::get_sus_questions(language = "en", questions_only = TRUE)) { -->
<!--   cat(paste0("1. ", q, "\n")) -->
<!-- } -->
<!-- ``` -->

```{r list_sus_questions}
usRbility::get_sus_questions(language = "en", questions_only = TRUE)
```

### Health IT Usability Evaluation Scale (Health-ITUES)

The Health-ITUES was described in 2010 and consists of `r get_health_itues_questions()[,.N]` questions [@yen2010a].

Its questions are:
```{r list_health_itues_questions}
usRbility::get_health_itues_questions(language = "en", questions_only = TRUE)
```

## More Infos

- About MIRACUM: <https://www.miracum.org/>
- About the Medical Informatics Initiative: <https://www.medizininformatik-initiative.de/index.php/de>

## References
